\section{Introduction}

% ------------------- Introduce Bayes --------------------------

Accurate revenue forecasting plays a pivotal role in the success of businesses,
aiding in efficient resource allocation, planning, and well-informed
decision-making. In this study, we delve into the application of Bayesian
models for predicting daily revenue at Copenhagen based poke bowl chain called
OLIOLI. By comparing the performance of various Bayesian models and evaluating
their usefulness, we aim to provide insights into the advantages and
limitations of these methods in a real-world context, and contribute to the
ongoing research in the field of Bayesian data analysis.
% Intuitive questions: Fixing observed data and updating beliefs about model parameters
Bayesian modeling, grounded in the principles of Bayes' theorem, provides an
alternative to the classic frequentist approach in data analysis and modeling.
In contrast to frequentist methods, which aim to estimate how likely observing
specific data is under the assumption of fixed model parameters, Bayesian
modeling is concerned with updating our beliefs about the model parameters
based on the data we observe. The key shift in conditioning on the data
instead of the model allows Bayesian methods to incorporate prior knowledge and
facilitate a more intuitive understanding of uncertainty, which can be
particularly useful for tackling complex real-world challenges.
% Handling uncertainty 
In practice, the prior belief is represented by a probability distribution over
the model parameters, which is updated to a posterior distribution after
observing data. This posterior distribution is then used to make predictions
and inferences about the model parameters. By their nature, probability
distributions are well suited to represent uncertainty 
% Model comparison and selection
% Additionally, the Bayesian method provides a principled framework for the comparison 
% and selection of different models. The best model for a problem is assumed to be 
% the most simple model able to explain the observed data and bayesian comparison methods 
% discussed in this paper provide a way to quantify this simplicity.

% ------------------- Define the problem --------------------------
% Daily revenue prediction
One area where modelling uncertainty is helpful is in revenue prediction and forecasting. 
This paper focuses on a case study to illustrate the application of Bayesian methods
and how the various decisions at steps of processing, modelling and comparison propegate 
to the final model and its predictions.
% Real-world phenomena complexity
When modelling real-world phenomena, the complexity of the problem can make it difficult 
to find a useful model - accurate and interpretable - and is therefore an exciting domain 
to test and evaluate theoretical methods.
% Revenue as a compound of individual human decisions
The revenue of a store is a compound of an immeasurable number individual human
decisions, which makes choosing the relavent, measurable variables of interest
a challenge. 
% Deciding on variables of interest: Expert opinion, domain knowledge, time series analysis
Here, we are guided by experts and their domain knowledge, who
have long been aware of the various temporal factors that influence revenue -
and what daily, weekly, and seasonal patterns mean for the business. The
weather thought to be another source of variablility throughout OLIOLI and it
was this that motivated the study of various weather phenomena on revenue.

% ------------------- Approaches to the problem -------------------

The problem of revenue forecasting is not a new one and there exist a number of
different approaches to time-sensitive prediciton, each with their own
subtleties to consider.
% Statistical modelling 
Traditional statistical modelling techniques are widely used to identify trends
and relationships between variables and make predictons and we will discuss how
Bayesian methods are a flexible extension of some of these methods. 
% Time series models
Working with time dependent data, time series models are a natural choice and
are widely used in industry for problems similar to the one this paper
addresses. Auto-regressive models, Moving Average models and everything in
between are some examples of time series which take a different approach to
modelling temporal data.
% Machine learning methods
Machine learning methods continue to grow in popularity, the applications of
which extend to a myriad of problems, no doubt including this one. The nature
of this problem prioritises interpretability over predictive power, which is
why we will not be comparing the specific implementations of these methods.
Nevertheless, the general principles of machine learning are worth mentioning
and recognising as a potential alternative to the methods discussed in this
paper.
% Bayesian approach: Advantages and challenges
And Bayesian modelling, the chosen tool central to this paper, can have a
number of benefits, such as the capacity to account for past knowledge,
quantify uncertainty, and automatically update the model when new data become
available. However, Bayesian methods can be computationally taxing,
particularly for large datasets and intricate models, and they might
necessitate a careful examination of prior distributions and presumptions.
% ------------------ Research Questions ----------------------------

In light of these approaches, the research questions that will be addressed in this paper are:

\begin{enumerate}
    \item What is the best performing Bayesian model for predicting daily revenue for OLIOLI with weather data?
    \item What is the optimal data volume for optimal revenue prediction?
    \item What are the assumptions and compromises of different models, and how do they impact the performance and the interpretability of the results?
\end{enumerate}

% ---------- Testing, evaluation, Bayesian comparison ------------

% Using real-world sales data for the case study
% Selection of the optimal model and data for specific problems
% Context-dependent decision-making
To answer these questions, we will test, compare and evaluate multiple Bayesian
models and evaluation metrics, using real-world sales data from OLIOLI. Current
research in the field exists for motivating the deployment of Bayesian models,
with methodologies existing for their evaluation and comparison. Despite this,
the exact process for selecting the optimal model and data for a specific
problem remains unclear and context-dependent.


% ------------------ Contributions -------------------------------

% Thorough testing, evaluation, and comparison of different assumptions in Bayesian data analysis
% Focus on revenue prediction for a restaurant chain
% Potential for accurate forecasting, better decision-making, and efficient resource allocation
The contributions of this paper are manifold, providing a comprehensive
testing, evaluation, and comparison of the different assumptions within the
realm of Bayesian data analysis; through the vessel of the mentioned case
study. By investigating the research questions and evaluating the performance
of various Bayesian models, this study aims to not only demonstrate the
potential for accurate forecasting but also emphasise the potential benefit of
informed decision-making and efficient resource allocation in a business
context.
% Hierarchical extension possibilities
